Pretty darn good control: when are approximate solutions better than approximate models

### 2022-11-29 manuscript/manuscript.Rmd
a little historical hat-tip :tophat:

---
title: Title here
subtitle: Do you have a subtitle? If so, write it here
titlerunning: Short form of title (if too long for head)
authorrunning: Short form of author list if too long for running head
thanks: | 
    Grants or other notes about the article that should go on the front 
    page should be placed here. General acknowledgments should be placed at the
    end of the article.

authors: 
- name: Äüthör 1
  address: Department of YYY, University of XXX
  email: abc@def

- name: Âuthóř 2
  address: Department of ZZZ, University of WWW
  email: djf@wef

keywords:
- key
- dictionary
- word

@@

bibliography: bibliography.bib
biblio-style: spphys
# bibstyle options spbasic(default), spphys, spmpsci
output: rticles::springer_article
---

@@

>>>>

---
title: "Pretty darn good control: when are approximate solutions better than approximate models"
titlerunning: Pretty darn good control
thanks: | 
    This material is based upon work supported by the National Science
    Foundation under Grant No. DBI-1942280.

authors: 
- name: Felipe Montealegre-Mora
  address: Department of Environmental Science, Policy, and Management, University of California, Berkeley
- name: Marcus Laperolerie
  address: Department of Environmental Science, Policy, and Management, University of California, Berkeley
- name: Melissa Chapman
  address: Department of Environmental Science, Policy, and Management, University of California, Berkeley
- name: Carl Boettiger
  address: Department of Environmental Science, Policy, and Management, University of California, Berkeley
  email: cboettig@berkele.edu

keywords:
- Optimal Control
- Reinforcement Learning
- Uncertainty
- Decision Theory

@@

bibliography: bibliography.bib
biblio-style: spphys

# bibstyle options spbasic(default), spphys, spmpsci
output: rticles::springer_article

---

@@

## Acknowledgements

The title of this piece references a mathematical biology workshop at NIMBioS
organized by Paul Armsworth, Alan Hastings, Megan Donahue, and Carl Towes in
2011 that first posed the question addressed here.

# References
